A thesis draft

### 2018-11-28 res/sections/15-ArchitecturalImplementation.tex
Fix errors in 15

\subsubsection{Dynamic package routing: the Roulette component}
\label{chap:prjan:sec:tech:sub:SFC:sub:roulette}
Dynamic end-to-end communications between VNFs would not be possible without a
third component acting as a route controller. Roulette fulfills this role,
providing a back-end where the single VNF can ask the next packet hop. Indeed,
routes must be submitted by another component, that we identified as Harbor.
After a NS deployment, Roulette gets instructed with a new route describing a
NS. Every NS has a proper ID (called \verb!sfid!), and thus when the classifier
checks a packet typology, it labels that packet with the specific NS ID (for a
detailed description about the SFC header see
Section~\ref{chap:background:sec:sfc}). Finally, thanks to this label, every VNF
knows the packet's chain and it will correctly forward the it to the next VNF.

@@

\subsubsection{A VNF framework: Astaire}
As is possible to denote, a VNF doesn't only process the incoming packets, but
it has to manage the communications and the related forward operations. To
possibly ease part of the transmission problems and to make it easier to create
a VNF without requiring the whole knowledge about SFC, we decided to build a
framework, Astaire, that could kept the SFC related details decoupled from the
core of the VNF, in other words, the entity that actually elaborates the packet.
Built using an event-based pattern, it presents hooks that allow other software
written in different languages from the Astaire one (e.g. Java), to be called
dynamically at runtime in order to process the packet. The result of this
elaboration gets returned to Astaire, that performs the beforehand cited
operations of VNFs communications and forwarding. In the SFC specification,
Astaire is defined as a Service Function Forwarder (SFF).

>>>>

\subsubsection{Dynamic package routing: the Roulette component}
\label{chap:prjan:sec:tech:sub:SFC:sub:roulette}
Dynamic end-to-end communications between VNFs would not be possible without a
third component acting as a route controller. Roulette fulfills this role,
providing a back-end where the single Service Function Forwarder (SFF) can ask
the next packet hop. Indeed, routes must be submitted by another component, that
we identified as Harbor. After a NS deployment, Roulette gets instructed with a
new route describing a NS. Every NS has a proper ID (called \verb!sfid!), and
thus when the classifier checks a packet typology, it labels that packet with
the specific NS ID (for a detailed description about the SFC header see
Section~\ref{chap:background:sec:sfc}). Finally, thanks to this label, every VNF
knows the packet's chain and it will correctly forward the it to the next VNF.

@@

\subsubsection{A Service Function Forwarder: Astaire}
As is possible to denote, an SFC-unaware VNF can not elaborate a packet directly
coming from an SFC. The packet coming from an SFC contains additional
information and metadata that have to be removed first. In this context, we
decided to build a framework, Astaire, that could kept the SFC related details
decoupled from the core of the VNF, in other words, the entity that actually
elaborates the packet. Built using an event-based pattern, it presents hooks
that allow other software written in different languages from the Astaire one
(e.g. Java), to be called dynamically at runtime in order to process the packet.
The result of this elaboration gets returned to Astaire, that performs the
beforehand cited operations of VNFs communications and forwarding. In the SFC
specification, Astaire is defined as a SFF.
